---
title: "Lab 6: MATH 4753"
author: "Hunter DeVoe"
date: "February 8, 2023"
output: 
  html_document:
    toc: yes
    toc_float: yes
    theme: spacelab
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(pacman, tidyverse, lattice, s20x, knitr, devtools, roxygen2, testthat)
```

# Task 1

```{r}
getwd()
```

# Task 2

## Use layout() to construct a plotting region that will take 4 plots. Use it to plot 4 normal curves with the following parameters.  

* $\mu = 10, \sigma = 4$  

* $\mu = 10, \sigma = 2$  

* $\mu = 5, \sigma = 10$  

* $\mu = 5, \sigma = \frac{1}{2}$

```{r}
layout(matrix(1:4, nr=2,nc=2))

curve(dnorm(x, mean=10,sd=4),xlim=c(-10,30))

curve(dnorm(x, mean=10,sd=2),xlim=c(-10,30))

curve(dnorm(x, mean=5,sd=10),xlim=c(-40,40))

curve(dnorm(x, mean=5,sd=1/2),xlim=c(0,10))
```

## Plot the following regions and probabilities using one graphical interface per plot (use 4 dec. places)  

* $Y \sim N(0, 1), P(Y \geq 2)$  

* $Y \sim N(\mu = 4, \sigma = 2), P(1 \leq Y < 5)$  

* $Y \sim N(\mu = 10, \sigma = 4), P(Y < 10)$  

* $Y \sim N(\mu = -2, \sigma = \frac{1}{2}), P(-3 < Y \leq -2)$

```{r}
layout(matrix(1:4, nr = 2, nc = 2))

# COMPLETE THIS!!!!
curve(dnorm(x, 0, 1), xlim = c(10 - 3.5, 10 + 3.5))

curve(dnorm(x, 4, 2), xlim = c(4 - 3.5, 4 + 3.5))
#P(1 <= y < 5)
area <- pnorm(5, 4, 2) - pnorm(1, 4, 2)
area <- round(area, 4)
xcurve <- seq(1, 5, length = 1000)
ycurve <- dnorm(xcurve, 4, 2)
polygon(c(1, xcurve, 5), c(0, ycurve, 0), col = "Red")
text(7, 0.15, paste0("Area = ", area))

# INSERT PLOT 3

curve(dnorm(x,-2, 0.5), xlim = c(-2 - 3.5, -2 + 3.5))
#P(-2 <= y < -1)
area <- pnorm(-1, -2, 0.5) - pnorm(-2, -2, 0.5)
area <- round(area, 4)
xcurve <- seq(-2, -1, length = 1000)
ycurve <- dnorm(xcurve, -2, 0.5)
polygon(c(-2, xcurve, -1), c(0, ycurve, 0), col = "Blue")
```

# Task 3  

## On the one plotting surface, overlay the following three plots:  

  * $Y \sim Gamma(shape = 1, scale = 1)$  
  
  * $Y \sim Gamma(shape = 3, scale = 1)$  
  
  * $Y \sim Gamma(shape = 5, scale = 1)$
  
```{r}
curve(dgamma(x,shape=1,scale=1),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2,
ylab="Gamma density", main="Beta=1")
text(1.1, .7, paste0("alpha = ",1))

curve(dgamma(x,shape=3,scale=1),xlim=c(0,10),ylim=c(0,1),add=TRUE, col = "Green", lwd=2)
text(2, .35, paste0("alpha = ",2))

curve(dgamma(x,shape=5,scale=1),xlim=c(0,10),ylim=c(0,1),add=TRUE, col="Blue",lwd=2)
text(4.5, .25, paste0("alpha = ",3))
```

## Plot the following regions and probabilities in R  

* $Y \sim Gamma(shape = 3, scale = 2), P(2 < Y < 5)$  

```{r}
curve(dgamma(x,shape=3,scale=2),xlim=c(3,5),ylim=c(0,1),col="Red",lwd=2,
ylab="Gamma density")
```

* $Y \sim Gamma(shape = 6, scale = 3), P(1 \leq Y \leq 4)$


```{r}
curve(dgamma(x,shape=6,scale=3),xlim=c(1,5),ylim=c(0,1),col="Red",lwd=2,
ylab="Gamma density")
```

$Y \sim Gamma(shape = 2, scale = 4) $

```{r}
curve(dgamma(x,shape=2,scale=4),xlim=c(3,6),ylim=c(0,1),col="Red",lwd=2,
ylab="Gamma density")
```









```{r}
# CLEAN UP #################################################

# Clear environment
rm(list = ls()) 

# Clear packages
p_unload(all)  # Remove all add-ons

# Clear plots
dev.off()  # But only if there IS a plot

# Clear console
cat("\014")  # ctrl+L

# Clear mind :)
```
